\cvsection{Experience}
\begin{cventries}
    \cventry
    {Amazon.com (AWS)}
    {Software Engineer Intern}
    {Seattle, WA}
    {May 2020 - Aug. 2020}
    {
        \begin{cvitems}
        \item{Worked with the \textbf{Amazon Connect} team, a \textbf{cloud-based} call center as a service product running on \textbf{AWS}}
        \item{Built a deployment pipeline for \textbf{Safe Dynamic Config (SDC)}}
            \begin{itemize}
                \item{Implemented strict templating and config generation to allow for configuration as code}
            \end{itemize}
        \item{Library to pull deployed \textbf{SDCs} from remote and parse them for \textbf{Feature Access Control (FAC)} (Java)}
            \begin{itemize}
                \item{Created this library from scratch -- library was not based on an existing codebase.}
                \item{Part of an existing effort to migrate \textbf{Feature Access Control} from a flat config file in \textbf{S3} to a fast, compartmentalized, safe, dynamic config \textbf{deployment as code}}
            \end{itemize}
        \item{Implemented a proof-of-concept utilizing the library to replace the existing \textbf{FAC} implementation}.
        \end{cvitems}
    }
    \cventry
    {Brown University}
    {Computer Science Teaching Assistant}
	{Providence, RI}
	{Sep. 2019 - Dec. 2019}
    {
        \begin{cvitems}
		\item{Undergraduate teaching assistant for \textbf{intermediate-level CS class}, CSCI 1270 - \textbf{Database Management Systems}}
        \end{cvitems}
    }
    \cventry
    {Leidos}
    {Software Engineer Intern}
    {Arlington, VA}
    {May 2019 - Aug. 2019}
    {
        \begin{cvitems}
        \item{Part of software development team working on \textbf{autonomous} (self-driving) sea vessels (C++/Python)}
        \item{Core member of \textbf{systems architecture} team for next-gen virtualization approach (VMWare/Red Hat/Kubernetes)}
            \begin{itemize}
                \item{Researched, evaluated, proposed, and implemented various architectures involving \textbf{VMWare} clustering, VMWare \textbf{vSAN}, Red Hat \textbf{OpenShift}, and \textbf{Kubernetes}}
                \item{Final proposed systems architecture approved for implementation}
            \end{itemize}
        \item{Major contributor of \textbf{software migration} process from Red Hat 6 to 7 (C++/Python)}
            \begin{itemize}
                \item{Significant code rewriting to fit a \textbf{microservice} approach}
            \end{itemize}
        \end{cvitems}
    }
    \cventry
	{Brown University}
	{Applied Mathematics Teaching Assistant}
	{Providence, RI}
	{Sep. 2018 - Dec. 2018}
    {
        \begin{cvitems}
		\item{Undergraduate teaching assistant for APMA 0340: Methods of Applied Mathematics II. This course covers both \textbf{nonlinear ordinary differential equations} and \textbf{partial differential equations} from an applied mathematics perspective.}
        \end{cvitems}
    }
    \cventry
	{FMS Inc.}
    {Software Engineer Intern}
    {McLean, VA}
    {May 2018 - Aug. 2018}
    {
        \begin{cvitems}
		\item{Cluster analysis in large-scale graphs (C\#)}
			\begin{itemize}
				\item{Researched, implemented, and \textbf{optimized} the \textbf{Markov Clustering Algorithm} (MCL) to identify clusters in relational graphs of size \textbf{100,000+} nodes and \textbf{120,000+} edges in less than \textbf{10 minutes}}
			\end{itemize}
		\item{Implemented secure, PCI-compliant payment integration on the web using Authorize.Net (ASP Classic)}
			\begin{itemize}
				\item{Complete integration with the \textbf{Authorize.Net} payment gateway, including both \textbf{one-time} payments and long-term customer \textbf{payment profiles}}
			\end{itemize}
        \end{cvitems}
    }
%    \cventry
%    {Teaching Assistant}
%    {Fairfax Collegiate}
%    {Reston, VA}
%    {Jun. 2017 - Aug. 2017}
%    {
%		\begin{cvitems}
%		\item{Summer enrichment program for elementary and middle school students}
%		\item{Taught classes focused around hardware/software development}
%		\end{cvitems}
%	}
%	\cventry
%	{Private Tutor}
%	{Physics Tutor}
%	{McLean, VA}
%	{Jul. 2017 - Aug. 2017}
%	{
%		\begin{cvitems}
%		\item{Covered AP Physics C: Mechanics -- included homework, assessments, and lecture captures}
%		\end{cvitems}
%	}
%    \cventry
%    {Smithsonian Institution}
%    {Software Engineering Intern}
%    {Washington D.C.}
%    {Jun. 2016 - Aug. 2016}
%    {
%        \begin{cvitems}
%		\item{Metadata extraction tool (Java/shell scripts)}
%        \begin{itemize}
%			\item{Reads \textbf{metadata} from files in an ingest folder and populates an \textbf{Oracle database} with the data}
%        \end{itemize}
%		\item{Metadata ingestion tool (Java)}
%        \begin{itemize}
%			\item{Automatically processes \textbf{spreadsheets} within ingest folders and populates \textbf{Oracle database}}
%        \end{itemize}
%        \end{cvitems}
%    }
%    \cventry
%    {Smithsonian Institution}
%    {Software Engineering Intern}
%    {Washington D.C.}
%    {Jun. 2015 - Aug. 2015}
%    {
%      \begin{cvitems}
%	  \item {Two-part data integrity program for Smithsonian Digital Asset Management System}
%        \begin{itemize}
%			\item {Ingests \textbf{MD5 checksum} data and writes it to an Oracle database, and \textbf{verifies data integrity} at a later date}
%        \end{itemize}
%      \end{cvitems}
%    }
%    \cventry
%    {Mobile App Content Creator and Application Tester}
%    {SmartNoter LLC}
%    {Fairfax, Virginia}
%    {Jun. 2014 - Aug. 2014}
%    {
%        \begin{cvitems}
%            \item{Produced educational videos using Camtasia}
%            \item{Worked with program managers to test application functions and improve user interface and experience}
%        \end{cvitems}
%    }
%    \cventry
%    {Mentor}
%    {Science Olympiad}
%    {Longfellow Middle School}
%    {2013-2017}
%    {
%        \begin{cvitems}
%		\item{Met with teams on a weekly basis -- prepared lesson plans, gave lectures, administered tests}
%        \item{Teams have won top awards at the state level every year}
%        \end{cvitems}
%    }
	\vspace{-1.0em}
\end{cventries}
